### 2025-05-25 conteudo/methods/methods.tex
add appendix with initial survey
add paragraph about contrib and remove some todo

For the teaching assistant and the student that executed the ArKanjo tool to explore duplications, 
we have asked them to answer some questions related to the experience of using the tool and what could be
improved. The questions asked is the following:

>>>>

For the teaching assistant and the student that executed the ArKanjo tool to explore duplications, 
we have asked them to answer some questions related to the experience of using the tool and what could be
improved. The survey with the users's answers can be found in Appendix \ref{app:survey}.

On a second stage of the Free Software Development course, we propose to students to contribute directly 
with the ArKanjo tool development without help from the tool creator, to verify if the tool can be a 
free software where multiple people can contribute. The tool's issue approached by the students where 
of our knowledge our pointed to us in the survey feedback. A total of three students forming two groups 
worked in direct contributions, a not a very expressive number compared with the initiate experiment.
